---
title       : Pediatrics Research Group
subtitle    : 10 February 2015
author      : Michael Ching, MD, MPH, FAAP
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Goals of Research Group

1. Increase productivity of researchers in department
2. Provide opportunities for new/current department members to perform research
3. Develop knowledge base of research resources at Tripler

--- .class #id 

## Publication Productivity

1. Survey of department in late 2014
2. PubMed "Tripler Pediatrics" (2012-)
3. Google Scholar "Tripler Pediatrics" (2012-)

[Link to Publication Bibliography](publications.html)

---

## Breakdown of Research Type

```{r, echo =FALSE}
library(ggplot2)
dat <- read.table("pubs_data.txt", sep = "\t", head = T)

ggplot(data=dat, aes(x=type)) + 
    geom_bar(fill="#FF9999", stat="bin") + xlab("Publication Type")  +
    theme(text = element_text(size=18))
```

---

## Participation by Residents

```{r, echo = FALSE}
ggplot(data=dat, aes(x=type, fill = resident)) + 
    geom_bar(stat="bin") + xlab("Publication Type") +
    theme(text = element_text(size=18))
```

---

## Key Figures

```{r, echo=FALSE}
dat$title <- as.character(dat$title)
dat$pinsker <- rep(F, length(dat$title))
suppressWarnings(dat$pinsker[grep("Pinsker", dat$title)] <- T)
dat$sawyer <- rep(F, length(dat$title))
suppressWarnings(dat$sawyer[grep("Sawyer", dat$title)] <- T)
dat$key_figs <- ifelse(dat$pinsker, "Pinsker", ifelse(dat$sawyer, "Sawyer", "Other"))
ggplot(data=dat, aes(x=type, fill = key_figs)) + 
    geom_bar(stat="bin") + xlab("Publication Type") +
    theme(text = element_text(size=18))
```

---

## Divisions Involved in Research

```{r, echo = FALSE}
ggplot(data=dat, aes(x=division)) + 
    geom_bar(fill="#FF9999", stat="bin") + xlab("Publication Type") +
    theme(text = element_text(size=18))
```

---

## Posters/Presentations

[Link to Posters/Conferences](posters_presentations.html)

---

## Conference Presentations
1. Lamphear, J. Military Medical Humanitarian Course: Malnutrition and Diarrhea and Dehydration in Complex Humanitarian Missions, Sept 2013, Seoul, South Korea.
Mahnke, CB. Tripler Army Medical Center Hospital Grand Rounds: Teleconsultation in the Pacific. Apr 2014.
1. Greene JP, Burr J: Teen Talk: How to Connect, Pediatrics Island Style, 2013, The Patient-Physician Relationship: Communication is Key, Honolulu, Hawaii, November 2013.
1. Woods, E. : Pediatric Windows Falls Prevention, Conference of the Western Pacific, Vancouver, WA, June 2014

---

## Funded Grants: 
1. Dobson, NR Effects of FGF2 in a Neonatal Mouse Model of White Matter Damage. Principal Investigator. Direct grant amount $60,000. Sponsor: USUHS Office of Research (funded 2011-2014). 
1. Dobson, NR Effect of Caffeine on Intermittent Hypoxia in Infants Born Preterm. Co-Investigator. Direct grant amount $90,000. Sponsor: American SIDS Institute (funded 2009-2014)
1. Ching, MSL. Development of a Collaborative Learning Site to Improve Assessment and Management of Developmental Behavioral Pediatrics Conditions, Principal Investigator. Direct Grant amount $20,000. Sponsor: TATRC (2014).
1. Pinsker, JE. 

---

## Research Group January Meeting
1. Discussed current research projects from Larson, Sampert, Ching, Chan
2. Created goal for each person to report back on (example: Sampert to update lit review for re-submission of research paper)
3. Opened project to find out what resources are available for database research

---

## Next Steps
1. Monthly research meeting
1. Encourage more active researchers' participation
2. Present research projects to residents to get them involved
3. Design, complete, and submit research